---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# digroot

[![Travis-CI Build Status](https://travis-ci.org/zkamvar/digroot.svg?branch=master)](https://travis-ci.org/zkamvar/digroot)

The goal of digroot is to calculate digital roots. A digital root is a single
digit that is obtained through a recursive sum of digits.

This package was inspired by a [Tweet from Thomas Morill](https://twitter.com/tsmorrill/status/1028108510746226688)

For example, the digital root of 77 is 5:

```{r digroot}
7 + 7
1 + 4
```

The *digroot* package automates this with the `dig_root()` function:

```{r dig_root}
digroot::dig_root(77)
```

It's also vectorized, which means that you can get the multiplication
table like so:

```{r multiply}
print(mult <- outer(1:9, 1:9))
matrix(digroot::dig_root(mult), ncol = 9, nrow = 9)
```

It can also work on really large numbers:

```{r bit}
set.seed(2018-08-12)
print(bignum <- paste0(sample(1e10, 100), collapse = ""))
digroot::dig_root(bignum)
```

> For reference, that number is `r paste0(substr(bignum, 1, 1), ".", substr(bignum, 2, 3), "e", nchar(bignum) - 1)`

You can find the immediate digital sum of a number by using the `dig_sum()`
function:

```{r dig_sum}
print(s   <- digroot::dig_sum(bignum))
print(ss  <- digroot::dig_sum(s))
print(sss <- digroot::dig_sum(ss))
```

## Installation

You can install digroot from github with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("zkamvar/digroot")
```

