---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# digroot

The goal of digroot is to calculate digital roots. A digital root is a single
digit that is obtained through a recursive sum of digits.

This package was inspired by a [Tweet from Thomas Morill](https://twitter.com/tsmorrill/status/1028108510746226688)

For example, the digital root of 77 is 5:

```{r digroot}
7 + 7 # 14
1 + 4 #  5
```

The *digroot* package automates this with the `dig_root()` function:

```{r dig_root}
digroot::dig_root(77)
```

You can find the immediate digital sum of a number by using the `dig_sum()`
function:

```{r dig_sum}
digroot::dig_sum(77)
digroot::dig_sum(14)
```

## Installation

You can install digroot from github with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("zkamvar/digroot")
```

